paper2_resistance_mechanisms_mixtures

### 2017-01-23 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
replace : with = in fig legends

### version 8

@@

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure: 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure: 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness2: 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness2: 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 1', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1: 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1: 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1: 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1: 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1: 1%', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1: 0.1%', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure: 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure:0.2', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

>>>>

### version 9

#An accessible model to help understand the evolution of insecticide resistance : insecticide effectiveness predicted to be key to the relative performance of mixtures.

#A tutorial, primer ...

@@

Good review of tactics for IRM inlcuding mention of mixtures and new AIs [@Denholm1992]
"Once developed and marketed, new products introduce a fresh challenge how to exploit their characteristics while restricting exposure to preserve their effectiveness."

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure = 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure = 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness2 = 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness2 = 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 1', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1 = 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1 = 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1 = 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1 = 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1 = 1%', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1 = 0.1%', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure = 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('male exposure =0.2', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r
